Strotor: A Minimalistic Approach to \\ Exploring Hierarchical Data

### 2014-04-16 paper/paper.tex
...

When the user starts the exploration, only the shops and categories
at the top level are displayed (Figure \ref{fig2}).
When the user generates {\D},
the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3}).

@@

We displayed {\ST} at an exhibition
held in November 2013, and asked more than 100 people to try it.
%
Since the only thing a user can do with {\ST} is rotating the device,
users seemed to be able to understand the behavior of {\ST} with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the users, but the hard restriction of the device seems to have worked in this case.

@@

>>>>

When the user starts the exploration, only the shops and categories
at the top level are displayed (Figure \ref{fig2}).
When the user generates {\D},
the second element (\tsf{Stationery store}) is selected (Figure \ref{fig3})\footnote{
  Readers can try this at \textsf{http://jsbin.com/lecuroku}.
}.

@@

We displayed {\ST} at an exhibition
held in November 2013, and asked more than 100 people to try it.
%
Since the only thing a user can do with {\ST} is to rotate the device,
users seemed to be able to understand the behavior of {\ST} with trials and errors.
% 
% a user can use the device and see what happens without thinking about
% other interactions.
% 
Using only one rotating device for data navigation is a new experience for
all the users, but the hard restriction of the device seems to have worked in this case.

\begin{figure}[H]
\centerline{\includegraphics[width=70mm,bb=0 0 527 329]{figures/c520d5dfbd06c532d48d324a7019b00c.png}}
\caption{Asking people to use Strotor at an exhibition. The subject is using PowerMate for browsing photos.}
\label{powermate}
\end{figure}

@@

We have developed a new very simple interaction method for exploring
large hierarchical data structure.
Using only one rotating device,
